---
title: "Task&7"
author: "Tyler"
date: "9/19/2022"
output: 
 html_document:
   keep_md: TRUE
---

```{r}
library(ggplot2)
library(readr)
library(knitr)
library(tidyverse)
library(dplyr)
library(forcats)
library(downloader)
```



```{r}
download.file("https://raw.githubusercontent.com/hadley/r4ds/master/data/heights.csv", "heights")

Height <- read_csv("heights")

Height

```


```{r}
HeightEd <- Height %>%
  mutate(ed = as.factor(ed)) %>%
  mutate(ed = fct_recode(ed,
                         "primary" = "3",
                         "primary" = "4",
                         "primary" = "5",
                         "primary" = "6",
                         "secondary" = "7",
                         "secondary" = "8",
                         "secondary" = "9",
                         "secondary" = "10",
                         "secondary" = "11",
                         "highschoolgrad" = "12",
                         "associates" = "13",
                         "associates" = "14",
                         "associates" = "15",
                         "bachelors" =  "16",
                         "mastersdoctorate" = "17",
                         "mastersdoctorate" = "18"))

```

```{r}
HeightEd1 <- HeightEd %>%
  group_by(race) %>%
  count(ed)

HeightEd1

```

```{r}
ggplot(HeightEd1, mapping=aes(ed,n, fill=race ))+
  geom_bar(stat="identity", position = "dodge")

```

```{r}
HeightEd2 <- HeightEd %>%
  group_by(sex) %>%
  count(ed)

HeightEd2
```

```{r}
ggplot(HeightEd2, mapping=aes(ed,n, fill=sex ))+
  geom_bar(stat="identity", position = "dodge")
```

```{r}
HeightEd3 <- HeightEd %>%
  group_by(race) %>%
  count(earn)

HeightEd3
```

```{r}
ggplot(data=HeightEd3, mapping=aes(x=earn,y=n, color=factor(race)))+
  geom_point()+
  labs(y="Number of people", x="Earnings")
```

In the data set above on the x axis it shows the amount earned by the indivual and on the y it shows the amount of indiviuals that earned it. THe different color points represent the race of the person or people at that point. What I learned is that white indivuals have a lot more top earners than any other race. Also even at low incomes white people have a lot more indviuals at those points than any other race. 

