---
title: "casestudy7"
author: "Tyler"
date: "10/10/2022"
output:  
  html_document:
   keep_md: TRUE
---
```{r}
library(tidyverse)
library(readr)
library(haven)
library(downloader)
library(foreign)
library(readxl)
```

```{r}
germancon <- read_dta(url("https://github.com/WJC-Data-Science/DTS350/blob/master/germanconscr.dta?raw=true"))
head(germancon)
germanprison <- read_dta(url("https://github.com/WJC-Data-Science/DTS350/blob/master/germanprison.dta?raw=true"))
head(germanprison)
height <- read_csv(url("https://raw.githubusercontent.com/hadley/r4ds/master/data/heights.csv"))
head(height)
height1 <- tempfile()
download("https://github.com/WJC-Data-Science/DTS350/blob/master/Height.xlsx?raw=true", height1, mode = "wb")
head(height1)
heightalt <- read_xlsx(height1, skip = 2)
head(heightalt)
heightse <- tempfile()
download("https://github.com/WJC-Data-Science/DTS350/raw/master/Heights_south-east/B6090.DBF?raw=true", heightse, mode = "wb")
head(heightse)
seheight <- read.dbf(heightse)
head(seheight)
```

```{r}
WisconsinData=read.spss("http://www.ssc.wisc.edu/nsfh/wave3/NSFH3%20Apr%202005%20release/main05022005.sav", to.data.frame=TRUE)
write.table(WisconsinData,"Wisconsin.csv")
head(WisconsinData)
```

```{r}
str(WisconsinData)
```


```{r}
heights_tidy <- heightalt %>%
  pivot_longer(3:203, names_to = "years", values_to = "heights.cm", values_drop_na = TRUE) %>%
  mutate(year_decade = years, height.in = heights.cm / 2.54) %>%
  separate(years, into = c("century", "decade"), sep = -2) %>%
  separate(decade, into = c("decade", "year"), sep = -1)
write.csv(heights_tidy, "heights_tidy.csv", row.names = TRUE)
```

```{r}
German_Con <- germancon %>%
  mutate(birth_year = bdec,
         height.cm = height,
         height.in = height.cm / 2.54,
         study_id = 'germanconscript') %>%
  select(birth_year, height.cm, height.in, study_id)
```

```{r}
German_Pri <- germanprison %>%
  mutate(birth_year = bdec,
         height.cm = height,
         height.in = height.cm / 2.54,
         study_id = 'germanprison') %>%
  select(birth_year, height.cm, height.in, study_id)
```

```{r}
heightdat <- height %>%
  mutate(birth_year = 1950,
         height.cm = height * 2.54,
         height.in = height,
         study_id = 'heights') %>%
  select(birth_year, height.cm, height.in, study_id)
```

```{r}
Southheight <- seheight %>%
  mutate(birth_year = SJ,
         height.cm = CMETER,
         height.in = CMETER / 2.54,
         study_id = 'se_heights') %>%
  select(birth_year, height.cm, height.in, study_id)
```

```{r}
Wisconsintidy <- WisconsinData %>%
  mutate(birth_year = as.numeric(DOBY) + 1900,
         height.cm = RT216I * 2.54,
         height.in = RT216I,
         study_id = 'WisconsinData') %>%
  select(birth_year, height.cm, height.in, study_id)
```



```{r}
combine <- bind_rows(German_Con,German_Pri,heightdat,Southheight,Wisconsintidy)
write.csv(combine, "Combined.csv", row.names = TRUE)
```

```{r}
germany_filter <- heights_tidy %>%
  filter(`Continent, Region, Country` == 'Germany')
```

```{r plot1}
ggplot(data = heights_tidy, aes(x = year_decade, y = height.in)) +
  geom_boxplot(alpha = 0.5) +
  geom_point(data = germany_filter, color = "red") +
  theme_bw() +
  labs(x = "Decade",
       y = "Height in.",
       title = "Heights Across Decades in Germany")
```
The plot above is a boxplot that shows the height distribution of people in the country of Germany. The boxplot helps us to see both where the average, above average, and below average heights are. It also gives a good representation of what the outliers are.  
```{r plot2}
ggplot(combine, aes(x = birth_year, y = height.in)) +
  geom_col() +
  facet_wrap(~ study_id, scales = 'free') +
  theme_bw() +
  labs(x = "Year",
       y = "Height Distribution",
       title="Is there a relationship between the data sets?")
```
The second graph shows all the data sets and the heights in all of them. It kind of hard to make an accurate conclusion here. But what we can say is that there seems to be an overall growth in height except for the mid 1800s. 