---
title: "Task14"
author: "Tyler"
date: "10/19/2022"
output:  
  html_document:
   keep_md: TRUE
---
```{r}
library(tidyverse)
library(knitr)
library(downloader)
library(dplyr)
library(lubridate)
library(ggplot2)
library(grid)
library(readr) 
library(haven)
library(readxl)
library(stringi)
library(stringr)
```



```{r}
bob <- tempfile()
download("https://raw.githubusercontent.com/WJC-Data-Science/DTS350/master/bible.csv", bob, mode = "wb")
bib1 <- read_csv(bob)
head(bib1)
str(bib1)
```

```{r}
old <- bib1 %>%
  filter(volume_long_title == "The Old Testament") %>%
  select(scripture_text)
head(old)
new <- bib1 %>%
  filter(volume_long_title == "The New Testament") %>%
  select(scripture_text)
head(new)
```

```{r }
versel <- function(df) {
  vlength <- vector("integer", 0)
  for(row in df) {
    vlength <- append(vlength, str_length(row))
  }
  vlength
}
```

```{r }
mean(versel(old))
mean(versel(new))
```

```{r}
str_length(str_extract_all(old, "(?i)lord"))
str_length(str_extract_all(new, "(?i)lord"))
```
```{r}
wordcount <- bib1 %>%
  mutate(word_count =
           sapply(bib1$scripture_text, function(x) length(unlist(strsplit(as.character(x), "\\W+"))))
  )
```

```{r}
new1 <- wordcount %>%
  subset(volume_id == 2)
mean(new1$word_count)
```

```{r}
ggplot(data = new1, aes(x = verse_number, y = word_count, fill = book_title)) +
  geom_col() +
  facet_wrap(~book_title, scales = 'free') +
  theme(legend.position = "none") +
  labs(x = "Verse Number",
       y = "Word Count",
       title = "New Testament Average Word by Verse")
```
This was certanly a hard code for me to do. So to answer the first question what is the average verse length, I made a function that counted the amount of verses in the old and new testement. For the secound question I used the string length function that we learned recently, and counted all the times lord was used between the old and new testiment. My hypothisis was that Lord was used a lot more in the old than the new, because Jesus was in the new testement. That seemed to be true. Finally I made a graph of the word average by verse in the new. This took some word but I jsut got the word count for the new testement and did it by the verse length. 

