---
title: "CaseStudy6"
author: "Tyler"
date: "10/3/2022"
output:  
  html_document:
   keep_md: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r plots1-3}
library(tidyverse)
plot1 <- ggplot(diamonds, aes(x=x)) + 
  geom_histogram() +
    labs(title = "Distribution of length in mm")
plot1
plot2 <- ggplot(diamonds, aes(x=y)) + 
  geom_histogram() +
    labs(title = "Distribution of width in mm")
plot2
plot3 <- ggplot(diamonds, aes(x=z)) + 
  geom_histogram() +
    labs(title = "Distribution of depth in mm")
plot3
```

```{r plot4}
plot4 <- ggplot(diamonds, aes(x = price)) + 
  geom_histogram() +
      labs(title = "Distribution of price")
plot4
```
It is unusual as the distribution for price is skewed to the cheaper side. It is odd considering dimonds are expensive. 

```{r plot5}
plot5 <- ggplot(diamonds, aes(x=carat, y=price)) + geom_point() +
      labs(title = "Price to Carat Size")
plot5
```
Carat seems to have the most effect on the price of the diamond. 

```{r plot6}
plot6 <- ggplot(diamonds, aes(x=carat, y=price, color=cut)) + 
  geom_point() +
      labs(title = "How the Carats and the Cut Lines Up")
plot6
```
It seems like the more ideal cuts are group at the lower end of the carats. 

```{r plot7}
plot7 <- ggplot(diamonds, aes(x=carat, y=price, color=clarity)) + 
  geom_point() +
      labs(title = "The Level of Clarity by Carat")
plot7
```
It seems that these grpahs above show us that the lower the carat the better quality of diamond. This includes the clarity and cut, which would lead to lower carat diamonds being more expensive.  

```{r plot8}
price_diamonds <- diamonds %>%
  mutate(groupprice = 
           case_when(
             price>=0 & price <= 2000 ~ "1-2000",
             price>=2001 & price <= 4000 ~ "2001-4000",
             price>=4001 & price <= 6000 ~ "4001-6000",
             price>=6001 & price <= 8000 ~ "6001-8000",
             price>=8001 & price <= 10000 ~ "8001-10000",
             price>=10001 & price <= 12000 ~ "10001-12000",
             price>=12001 & price <= 14000 ~ "12001-14000",
             price>=14001 & price <= 16000 ~ "14001-16000",
             price>=16001 & price <= 18000 ~ "16001-18000",
             price>=18001 & price <= 20000 ~ "18001-20000"),
         groupprice = fct_relevel(groupprice,
"1-2000","2001-4000","4001-6000","6001-8000","8001-10000","10001-12000","12001-14000","14001-16000","16001-18000","18001-20000"))
head(price_diamonds)
plot8 <- ggplot(price_diamonds, aes(x = groupprice, y = carat, fill = groupprice)) +
  geom_boxplot() +
  coord_flip() +
  theme_bw() +
  labs(title = "The number of carats in groups of prices")
plot8
```

```{r plot9}
plot9 <- diamonds %>% 
  filter(carat>=4.0) %>%
  group_by(carat) %>% 
  ggplot(aes(x = price)) +
  geom_histogram() +
  theme_bw() +
  labs(title = "The Price of Very Large Diamonds")
plot10 <- diamonds %>% 
  filter(carat<=1.5) %>%
  group_by(carat) %>% 
  ggplot(aes(x = price)) +
  geom_histogram() +
  theme_bw() +
  labs(title = "The Price of Very Small Diamonds")
plot9
plot10
```
This is pretty predictable, as the bigger carats leads to hgiher prices. There are very few big diamonds, but of them, they are much more expensive than the small ones.  

```{r plot11}
plot11 <- ggplot(diamonds, aes(x = price, y = carat, color)) + 
  geom_col() +
  facet_wrap(~cut, ncol=5) +
  theme_bw() +
  theme(axis.text.x = element_text(face="bold", 
                           size=8, angle=45)) +
  coord_cartesian(ylim = c(0, 12), expand = TRUE) +
  labs(title = "Cut, Carat, and Price")
plot11
```
