---
title: "Case12"
author: "Tyler"
date: "11/28/2022"
output: 
  html_document:
   code_folding: "hide"
   keep_md: TRUE
---

```{r}
library(tidyverse)
library(sf)
library(USAboundaries)
library(ggplot2)
library(readr)
library(knitr)
library(tidyquant)
library(dplyr)
library(forcats)
library(downloader)
library(corrplot)
library(ggrepel)
library(sf)
library(maps)
library(readr)
library(remotes)
library(dygraphs)
library(ggsflabel)
library(plotly)
library(gridExtra)
library(gganimate)
library(leaflet)
library(maps)
library(grid)
```


```{r}
avocado <- read_csv("avocado.csv")
head(avocado)
tail(avocado)
```


```{r}
region <- avocado %>% distinct(region)
```

#Region 
```{r}
regions <- c("West", "Midsouth", "Northeast", "SouthCentral", "Southeast", "GreatLakes", "Plains")
avocado_regions <- avocado %>%
  filter(region == regions)
head(avocado_regions)
```
unique(avocado$region)

#City
```{r}
cities = c("Albany", "Boston", "Chicago", "Denver", "Jacksonville", "NewYork", "Philadelphia", "Portland", "Sacramento", "StLouis", "Atlanta", "Detroit", "LasVegas", "SanDeigo", "Syracuse", "Columbus", "Houston", "GrandRapids", "LosAngeles", "Nashville", "Pittsburgh", "SanFrancisco", "Tampa", "SanDi", "Boise", "Charlotte", "Indianapolis", "Louisville", "Orlando", "Roanoke", "Seattle", "Spokan")
avocado_cities <- avocado %>%
  filter(region == cities)
```



#Total 
```{r}
unique(avocado$region)
avocado_us <- avocado %>%
  filter(region == "TotalUS")
head(avocado_us)
```
#Avocado Prices over Time 
```{r}
total_us_plot <- ggplot(data = avocado_us, mapping = aes(x =Date, y =AveragePrice, color =year)) +
  geom_line() + 
  labs(title = "Average Avocado Prices from 2015 to 2018", subtitle = "Data Source=Total of U.S", x = "Date", y = "Average Price") 
total_us_plot
total_us_plot + transition_reveal(Date)
```
#It is worth noting that the price of the avacado is not static, and seems to constantly be changing over time

#Avocado Prices for US Regions Plot
```{r}
price_region_plot <- ggplot(data = avocado_regions, mapping = aes(x = Date, y = AveragePrice, color = `Total Volume`)) +
  geom_point() + 
  labs(title = "Average Avocado Prices from 2015 to 2018 with respect to volume", subtitle = "Data Source=Regions", x = "Date", y = "Average Price") + transition_time(Date)
price_region_plot
```
#It seems that there is a lot more volume when the price is lower. This makes sense as more people buy avocados when they are cheap 

#Avocado Prices for Each US City 
```{r}
price_city_plot <- ggplot(data = avocado_cities, mapping = aes(x = Date, y = AveragePrice, color = `Total Volume`)) +
  geom_line() +
  facet_wrap(~region) +
  labs(title = "Average Avocado Prices", subtitle = "From Each US City", x = "Date", y = "Average Price")
price_city_plot 
```
#Iw would tell the friend to not live in San Francisco, New York, Chicago, and Jacksonville. The best spot would be columbus, Atlanta, Pittburg, and Nashville. 


#I did the rest of this case on a seprate document beacuse it will not run. 

