---
title: "Case11"
author: "Tyler"
date: "11/14/2022"
output: 
  html_document:
   code_folding: "hide"
   keep_md: TRUE
---

```{r}
library(tidyverse)
library(sf)
library(USAboundaries)
library(ggplot2)
library(readr)
library(knitr)
library(tidyverse)
library(dplyr)
library(forcats)
library(downloader)
library(corrplot)
library(ggrepel)
library(sf)
library(maps)
library(readr)
library(remotes)
library(dygraphs)
library(ggsflabel)
library(plotly)
library(gridExtra)
library(leaflet)
```

```{r}
permits_data <- tempfile()
download("https://raw.githubusercontent.com/WJC-Data-Science/DTS350/master/permits.csv", 
         permits_data, mode = "wb")
permits <- read_csv(permits_data)
head(permits)
```
```{r}
filterPA<- permits %>%
  filter(StateAbbr=="PA",year==2010)
head(filterPA)
```

```{r}
county1 <- read_csv("CountyDat.csv")
head(county1)
permitsPA<-filterPA %>%
  mutate(county = as.character(county))
head(permitsPA)
county2<-county1 %>%
  mutate(county=as.character(`County Code Number`))
head(county2)
```

```{r}
combine<- left_join(county2, permitsPA, by="county")
head(combine)
```




```{r}
combine1 <- combine %>%
  arrange(desc(value))
head(combine1)
```

```{r}
topcounty <- combine1 %>%
  filter(row_number() == 1)
topcounty
```


```{r}
PA <- us_counties(states = 'PA')
PAcounties <- ggplot(PA) +
  geom_sf()
PAcounties
```


```{r}
combine1$quartile <- ntile(combine1$value, 4)
combine1
```
Quartile 4 is top 25%
Quartile 3 is top 25-50%
Quartile 2 is bottom 25-50%
Quartile 1 is bottom 25%
```{r}
ntile4<- combine1%>%
  filter(quartile==4)
ntile3 <- combine1%>%
  filter(quartile==3)
ntile2<- combine1%>%
  filter(quartile==2)
ntile1 <- combine1%>%
  filter(quartile==1)
```


```{r}
leaflet() %>%
  addTiles() %>%
  addCircleMarkers(data = ntile4,radius = 7,color = "blue",stroke = FALSE,fillOpacity = 1,popup = ~county,label = ~value)%>%
addCircleMarkers(data = ntile3,radius = 7,color = "red",stroke = FALSE,fillOpacity = 1,popup = ~county,label = ~value)%>%
addCircleMarkers(data = ntile2,radius = 7,color = "yellow",stroke = FALSE,fillOpacity = 1,popup = ~county,label = ~value)%>%
addCircleMarkers(data = ntile1,radius = 7,color = "green",stroke = FALSE,fillOpacity = 1,popup = ~county,label = ~value)
```

#So to ge this code to work I first had to make sure that joining the two datasets together would work. To do that I simply mutated each set so that the country codes were chacters and bith said county. I also had to get just pennsilvania for the main permits dataset. Once they were joined I used the entile functin to find the 4 quateriles that the question was looking for. Once I did that I used leaflet to drop all the pins on each county. For some reason there are multiple values for some counties and I was unable and unsure how to adress that. 